Considering scale in multilayer animal social networks

### 2020-06-29 paper/manuscript.Rmd
box edits

# Box 1
<!-- Finally, due to the autocorrelated nature of biologging data it is -->
<!-- essential to ensure social association data area non-randomly distributed -->
<!-- [@Farine_2017b]. -->

<!-- TODO include mov elsewhere 
Social processes, movement decisions, and space use are inextricably linked and
multilayer networks represent a potential analytical framework for linking these
processes [@Mourier_2019].

Integrating habitat-specific
movement layers could further illuminate the role of movement as a driver of the
social and spatial environments an individual experiences [@Webber_2018]. 
-->

Social phenotype has been increasingly linked to individual fitness, including
in primates [@Brent_2017; @Thompson_2019], dolphins [@Stanton_2012;
@Stanton_2011], and birds [@McDonald_2007; @Royle_2012]. Social and temporal
scales have emerged as important variables for understanding the fitness
consequences of social network position [@Almeling_2016; @Berger_2015;
@Brent_2017; @Holekamp_2011].

Varying social scales can have different fitness repercussions for individuals.
Rhesus macaques (*Macaca mulatta*) had higher survivorship when they had fewer
but stronger and more stable social associates and grooming partners rather than
simply more associates [@Ellis_2019].  It is a common trope that individuals
must be associating to interact, and many studies assume that proximity is proxy
for interacting [@Farine_2015a]. For instance, baboons must be within proximity
of each other for grooming yet other animals interact using communication
such as long-distance vocalization or olfactory signals 
[@Carter_2015]. It is possible to record social interactions that do not require
proximity using, for example, microphone arrays to construct long-distance
communication networks [@Snijders_2017].

Multilayer networks enable researchers to look at similarities and differences
between discrete temporal windows. Changing social phenotypes over ontogeny can
affect fitness [@Berger_2015; @Brent_2017]. Individuals progress through
development at different rates [@Tarka_2018] and this variation can complicate
the selection of time windows. Considering fine temporal scales provides insight
across developmental stages that may otherwise be missed [@Turner_2020]. Thus,
it is critical to carefully consider the effect of scale on the relationship
between an individual’s social network position and fitness using a temporal
scale based on the hypotheses being tested and logistical constraints.

>>>>

# Box 1
Social phenotype has been increasingly linked to individual fitness, including
in primates [@Brent_2017; @Thompson_2019], dolphins [@Stanton_2012;
@Stanton_2011], and birds [@McDonald_2007; @Royle_2012]. Social and temporal
scales have emerged as important variables for understanding the fitness
consequences of social network position [@Almeling_2016; @Berger_2015;
@Brent_2017; @Holekamp_2011].

Varying social scales can have different fitness outcomes for individuals.
Rhesus macaques (*Macaca mulatta*) had higher survivorship when they had fewer
stable social associates and grooming partners compared to many weak social 
associates [@Ellis_2019]. Typically individuals
must be associating to interact, and many studies assume that proximity is proxy
for interacting [@Farine_2015a]. For instance, baboons (*Papio* spp.) must be 
within close proximity of each other for grooming yet, other forms
of social interaction may occur over long-distances based on vocal or
olfactory signals [@Carter_2015]. It is possible to record social interactions that do not require
proximity using, for example, microphone arrays to construct long-distance
communication networks [@Snijders_2017].

Multilayer networks enable researchers to investigate similarities and differences
in social processes between discrete temporal windows. Changing social phenotypes over ontogeny can
affect fitness [@Berger_2015; @Brent_2017]. Individuals progress through
development at different rates [@Tarka_2018] and this variation can complicate
the selection of time windows. Considering fine temporal scales provides insight
across developmental stages that may otherwise be missed [@Turner_2020]. It remains
critical to carefully consider the effect of scale on the relationship
between an individual’s social network position and fitness using a temporal
scale based on the hypotheses being tested and logistical constraints.
